Cosmological constraints from the redshift dependence of the galaxy angular 2-point correlation function

### 2016-10-06 draft/draft0.tex
updates

\shorttitle{Reshift Dependent Volume effect}
\shortauthors{X.-D. Li, C. Park, C.G. Sabiu, H. Park, D.H. Weinberg, J. Kim, S.E. Hong}

@@

\author{Xiao-Dong Li, }
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
\author{Cheng Cheng, }
\affil{Kavli Institute for Theoretical Physics China, Institute of Theoretical Physics, Chinese Academy of Sciences, Zhong Guan Cun Street 55\#, Beijing, 100190, P.R. China}
\affil{University of Chinese Academy of Sciences, P.R. China}
\author{Changbom Park,}
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
\author{Hyunbae Park, Cristiano G. Sabiu, }
\affil{Korea Astronomy and Space Science Institute, Daejeon 305-348, Korea}
%\author{David H. Weinberg,}
%\affil{Department of Astronomy and CCAPP, The Ohio State University, 140 West 18th Avenue, Columbus, OH 43210, USA}
%\author{Donald P. Schneider,}
%\affil{Department of Astronomy and Astrophysics, The Pennsylvania State University, 
%University Park, PA 16802 }
%\affil{Institute for Gravitation and the Cosmos, The Pennsylvania State University, 
%University Park, PA 16802 }
\author{Juhan Kim\altaffilmark{1},}
\affil{Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 130-722, Korea}
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
\and
\author{Stephen Appleby, Sungwook E. Hong}
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}

@@

\begin{abstract}
We propose to use the redshift of the shape of galaxy angular 2-point correlation function (2pCF) to constrain cosmology.
The method is a continue of our series of works \citep{Li2014,Li2015,Li2016} probing the redshift dependence of Alcock-Paczynski effect and volume effect. 
A wrongly adopted cosmology result in redshift-dependent mis-scaling in the constructed galaxy distribution,
which leads to redshift-dependent rescaling in the measured angular 2pCF.
We test our method on the HR4 mock galaxies having 457, 406, 352, 206 and 228 million galaxies at redshfits 0, 0.5, 1, 1.5, 2,
and find the redshift evolution of the scaling of angular 2pCF is sensitive to the adopted cosmological parameters and 
relatively insensitive to the gravitational growth of structure,
the galaxy bias, and the redshift space distortion.
Analyzing redshift evolution of the shape of 2pCF on scales $5  h^{-1} {\rm Mpc} \leq r_\perp \leq 40 h^{-1} {\rm Mpc}$ we derive tight constraints on $\Omega_m$ and $w$.
Our method is complementary to current works using 2pCF to constrain cosmological parameters.
The method could be applicable to future photometric surveys of DES, LSST to derive tight cosmological constraints.

\end{abstract}

@@

@@

\begin{figure*}
   \centering{
   \includegraphics[height=8cm]{fig1_a.eps}
   \includegraphics[height=8.5cm]{fig1_b.eps}
   }
   \caption{\label{fig_xyquan}
   %Apparent distortion of objects in four wrongly assumed cosmologies, assuming a true cosmology of .
   The scaling in four wrongly assumed cosmologies ..., % $\Omega_m=0.41$, $w=-1.3$ and $\Omega_m=0.11$, $w=-0.7$, 
   assuming a true cosmology of $\Omega_m=0.26$, $w=-1$.
   Left panel shows a series objects distributes as five perfect squares, measured by an observer located at the origin.
   Their true positions and shapes are plotted in blue dashed lines.
   The observer measures the redshifts of these objects, adopts the wrong cosmologies to compute the distance,
   and obtains wrong results (the red solid lines).
   %The red solid lines show their positions and shapes when the wrong cosmologies 
   % are assumed to compute distance from measured redshift.
   %The mis-estimation of angular diameter distance lead to wrong 
   Right panel shows the mis-estimation of angular diameter distance when the wrong cosmologies are adopted.
   %In our mock surveys we split the samples at $z=0.3$, 0.6, 0.9 and 1.2, as marked by the vertical lines.
   %measured by an observer located at the origin.
   %For reference, blue dashed squares show their shapes and positions in the true cosmology.
   }
   % Need a better plot to show angular size variation!!!
\end{figure*}

@@

In case wrong values of $\Omega_m$ and $w$ are adopted, 
the inferred $\Delta r_{\parallel}$ and $\Delta r_{\perp}$ are wrong,
resulting in wrong estimation in the object's shape (AP effect) and size (volume effect).
These effects and their cosmological consequences have been investigated in \cite{Li2014,Li2015,Li2016}.

In this paper we focus on the mis-estimation of the angular size $\Delta r_{\perp}$. %scaling of angular size,
The ratio of mis-estimation is
\begin{equation}\label{eq:DA}
 %{\rm Degree\ of\ volume\ magnification \equiv}
 %{\rm rat}_{\rm volume\ mag}\equiv
 \alpha_{\perp} \equiv \frac{\Delta r_{\perp, \rm wrong}}{\Delta r_{\perp, \rm true}}
 = \frac{D_{A, \rm wrong}}{D_{A, \rm true}},
\end{equation}
where ``true'' and ``wrong'' denote the values of $D_A$ in the true cosmology and wrongly assumed cosmologies, respectively.

An illustration is provided in the left panels of Figure \ref{fig_xyquan}.
Suppose that the true cosmology is a flat $\Lambda$CDM with present matter ratio $\Omega_m=0.26$
and standard dark energy EoS $w=-1$.
If we were to distribute a series of perfect squares at various distances ranging from 500 Mpc/h to 3\,000 Mpc/h,
and an observer located at the origin were to measure their redshifts and infer the sizes of the squares
using the distance-redshift relations of four incorrect cosmologies
\begin{eqnarray}
 & &{\rm (i)}.\ \Omega_m=0.40,\ w=-1.0, \nonumber \\ 
 & &{\rm (ii)}.\ \Omega_m=0.15,\ w=-1.0, \nonumber\\ \noindent
 & &{\rm (iii)}.\ \Omega_m=0.26,\ w=-0.5,\nonumber\\ \noindent
 & &{\rm (iv)}.\ \Omega_m=0.26,\ w=-1.5,  \nonumber \noindent 
\end{eqnarray}
as a result, 
the shapes of the squares appear distorted (AP effect),
and their sizes are wrongly estimated (volume effect).
Cosmological models (i,iii) yield to compressed size (in both angular and LOS direction),
and the degree of compression increases with increasing distance;

The mis-estimation of angular size, ${\Delta r_{\perp, \rm wrong}}/{\Delta r_{\perp, \rm true}}$, 
are displayed in the right panel of Figure \ref{fig_xyquan}.
All cosmologies, ${\Delta r_{\perp, \rm wrong}}/{\Delta r_{\perp, \rm true}}$ evolves a lot in the redshift range $0<z<2$.
As an example, when adopting the quintessence cosmology $\Omega_m=0.26,\ w=-0.5$,
the angular size is underestimated by 
%12.5\%, 17.7\%, 20.1\%, 21.3\%
8.9\%, 12.3\%, 13.6\%, 14.1\% 
at $z=0.5,1,1.5,2$.

@@

In sum, as a consequence of incorrectly adopted cosmologies, 
the size of the objects is mis-estimated and the magnitude of mis-estimation depends on the redshift.
In this paper we use the galaxy angular 2pCF to probe the mis-estimation of angular size ${\Delta r_{\perp, \rm wrong}}/{\Delta r_{\perp, \rm true}}$.

@@

The resulting mock galaxies was found to reproduce the 2pCF of SDSS DR7 volume-limited galaxy sample \citep{zehavi2011} very well \citep{hong2016}.
The mock galaxies shows a similar finger of god (FOG) feature \citep{FOG} as the observation.
The projected 2pCF of the mock and observational samples agree within 1$\sigma$ CL
on scales greater than 1 ${h^{-1}}$Mpc.

%As will be introduced in the next section, 
%The output of HR4 simulation includes one all-sky light cone mock galaxy catalogue reaching $r=3\,150$ ${h^{-1}}$Mpc 
%and a series ({\bf how many?}) of snapshot mock galaxy catalogues at different redshifts.
In this analysis we use snapshot data of HR4 galaxies at $z=0,0.5,1,1.5,2$.
%We require subhalos to have at least 30 member particles, 
%so the minimal mass of galaxies is $\simeq m_{p} \simeq 2.7 \times 10^{11} \hMsun$.
Setting a minimal halo mass of $3\times 10^{11} \hMsun$, 
%$4.57\times 10^8$, $4.06\times 10^8$, $3.52\times 10^8$, $3.06\times 10^8$ and $2.28 \times 10^8$ mock galaxies,
we select 457, 406, 352, 206 and 228 million mock galaxies at the five redshifts,
corresponding to a number density of 
%$1.46\times 10^{-2}$, $1.30\times 10^{-2}$, $1.13\times 10^{-2}$, $0.98\times 10^{-2}$ and $0.73\times 10^{-2}\ (h^{-1} \rm Mpc)^{-3}$,
1.46, 1.30, 1.13, 0.98 and 0.73 in unit of $ 10^{-2} h^{3} \rm Mpc^{-3}$,
%$1.46\times 10^{-2}$, $1.30\times 10^{-2}$, $1.13\times 10^{-2}$, $0.98\times 10^{-2}$ and $0.73\times 10^{-2}\ (h^{-1} \rm Mpc)^{-3}$,
respectively.
By applying a uniform mass cut, at higher redshift we are selecting less galaxies with larger galaxy bias.

As an illustration, Figure \ref{fig_scatter} displays the 2D distribution of a subsample of mock galaxies in five redshifts,
with $x$, $y$ coordinates computed using the ``correct'' values of cosmological parameters $\Omega_m=0.26,\ w=-1$ (left panels) 
and a wrong set of cosmological parameters $\Omega_m=0.05,\ w=-1.5$ (right panels), respectively.

When the correct cosmology is adopted the cosmic scale is correctly estimated in five redshifts.
The only factor leads to evolution of galaxy distribution with redshift is the gravitational growth of structure.
With the decreasing the redshift, we clearly see how the clusters and filaments form and grow.
On the other hand, when the wrong cosmology is adopted, there is an artifical scaling of scales in the constructed map.
The separations among galaxies are over-estimated by 
$25.6\%,47.3\%,62.2\%,71.7\%$ at redshifts of $0.5,1.0,1.5,2.5$,
leading to a clear evolution of the sizes of structures with redshift.

The growth of structure leads to growth of clustering strength of structures on all scales,
while the volume effect maintain the clustering pattern and uniformly re-scale all the structures.
Their imprints on the large scale structure is different and should be distinguishable in the statistical analysis.
In the following, we show that they affect the angular correlation function measurements in different ways, 
and can be easily separated.

@@

The growth of structure also make the size of structures evolves with redshift.
In the next subsection we will discuss how to distinguish these two effects in the galaxy angular 2pCF.

\begin{figure*}
   \centering{
   %\includegraphics[height=5.9cm]{fig8_0.eps}
   %\includegraphics[height=5.9cm]{fig8_wrongcos_0.eps}
   %\includegraphics[width=16cm]{fig2.eps}
   %\includegraphics[width=16cm,natwidth=8,natheight=14]{fig2.pdf}
   \includegraphics[width=16cm]{fig2.eps}
   }
   \caption{\label{fig_scatter}
  blah
   }
   % Need a better plot to show angular size variation!!!
\end{figure*}

@@

We use the angular 2pCF as a statistical tool to probe the volume effect.
The galaxy 2pCF as a function of galaxy separation in the angular direction, $\omega(r_\perp)$, is computed for snapshot data of mock galaxies at five redshifts.
We adopt the Landy-Szalay estimator~\citep{1993ApJ...412...64L},
\begin{equation}
\omega(r_\perp)=\frac{DD-2DR+RR}{RR}\ ,
\end{equation}
where $DD$ is the number of galaxy--galaxy pairs, 
$DR$ the number of galaxy-random pairs, 
and $RR$ is the number of random--random pairs, 
all separated by a distance defined by $r_\perp\pm\Delta_{r_\perp}$ where we choose $\Delta_{r_\perp}=1h^{-1}\rm Mpc$.
The random catalogue consists of unclustered points uniformly distributed in a same size box. 
In an effort to reduce the statistical variance of the estimator, we use 50 times as many random points as we have galaxies.

Considering the large number of galaxies and random points the 2pCF is computed part by part in subsamples with 
size of 1575 $h^{-1}{\rm Mpc}\times 1575\ h^{-1}{\rm Mpc}\times 105\ h^{-1}{\rm Mpc}$.
The Z direction with thickness $105\ h^{-1}\rm Mpc$ is treated as the radial direction (the $r$ direction) 
and the X-Y directions with each of width $1575 h^{-1}\ \rm Mpc$ are the angular plane.
For our simulation box size we can have 120 such subsamples.
The average of the measurements in all subsamples is adopted as the 2pCF of the whole sample,
while the covariances of them are adopted as the covariance matrix after multiplying a factor of $1/\sqrt{119}$.

\subsection{Galaxy angular 2pCF: amplitude and shape at different redshifts}\label{sec_2pCF_diffz}

\begin{figure*}
   \centering{
%   \includegraphics[width=18cm]{fig9_0.eps}
%   \includegraphics[width=18cm]{fig9_1.eps}
%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
%    \includegraphics[height=8cm]{smu.eps}
    \includegraphics[width=18cm]{fig3.eps}
    \includegraphics[width=18cm]{fig3_b.eps}
   }
   \caption{\label{fig_diffz}
  2pCF at different redshfits.
   }
\end{figure*}

The upper-left panel of Figure \ref{fig_diffz} displays the angular 2pCF measured from HR4 mock galaxies. % (multiplied by scale $r$) in the five snapshot.
We multiply $\omega$ by the separation $r_\perp$ to have similar amount of statistical uncertainty on all scales.

At different redshifts, we see large evolution in the amplitude of $\omega(r_\perp)$.
The amplitude of 2pCF is proportional to the clustering strengh which is affected by the gravitational growth of structures and the bias of the galaxies.
The amplitude is highest at $z=0$ where the large scale structures experienced most gravitational growth,
and also gets higher at $z>1$ with increasing redshift as a reason of more biased galaxies at higher redshift.
%leading to stronger clustering strength and higher amplitude of 2pCF.
%On the contrary, at higher redshift we find $\omega(z=2)>\omega(z=1.5)>\omega(z=1)$,
%The trend is different from $z=1,1.5,2$,
%simply because by applying a uniform mass cut we are selecting more biased galaxies at higher redshift.

Different from the large variation of amplitude among the different redshifts, %The shape of $r_\perp\omega$ also evolves with redshift.
the shape of $r_\perp\omega$ maintains similar at all redshifts;
it always peaks at $r\sim9 h^{-1}\rm Mpc$ and monotonically drops at larger or smaller scales.
The only exception is the small enhancement at $r\lesssim 2 h^{-1}\rm Mpc$,
which is caused by the non-linear growth of structures on small scales 
and is much more significant at lower redshfit.

In order to directly compare the shape of 2pCF at different redshifts,
in the middle panel of Figure \ref{fig_diffz} we show the $r_\perp\omega$ normalized by the overall amplitude within $5h^{-1}{\rm Mpc} < r < 50h^{-1}{\rm Mpc}$
(here after $\hat \omega_{r_\perp}$):
\begin{equation}
 \hat \omega_{ r_\perp} \equiv  \frac{ {r_\perp\omega}(r_{\perp})}{ \int_{r_{\perp, \rm min}}^{r_{\perp, \rm max}}r_{\perp} \omega(r_{\perp}) d r_{\perp} / (r_{\perp,\rm max}-r_{\perp,\rm min}) },
\end{equation}
where we choose $r_{\perp, \rm min}=5 h^{-1}$ Mpc, $r_{\perp, \rm max}=40 h^{-1}$ Mpc in this analysis.
Scales of $r_{\perp, \rm min}<5 h^{-1}$ Mpc are affected by non-linear growth of strucutre, 
the mis-estimation of whose contribution may lead to systematic errors in the derived cosmological constraints.
On scales larger than $40 h^{-1}$ Mpc it is may be possible to have precise analytically modelling the shape of the 2pCF
 \citep{Salvador2014,Salvador2016} which should be able to extract more cosmological information than our method 
(although out method should is also applicable).

The nice overlapping of the five redshift results
justify the small evolution of shape with redshift.
In the right panel, we further show the residual evolution of $\hat r_\perp\omega$ at high redshifts 
with respect to $z=0$.
There is only 1-4\% relative enhancement 
at $r<10h^{-1}\rm Mpc$,
and $<1.5\%$ relative suppression at $r>25 h^{-1}\rm Mpc$.
The trend is monotonic with redshift.

>>>>

\shorttitle{Reshift Dependent Volume effect}
\shortauthors{X.-D. Li, C. Cheng, C. Park, C.G. Sabiu, H. Park, J. Kim, S.E. Hong}

@@

\author{Xiao-Dong Li, }
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
\author{Cheng Cheng, }
\affil{Kavli Institute for Theoretical Physics China, Institute of Theoretical Physics, Chinese Academy of Sciences, Zhong Guan Cun Street 55\#, Beijing, 100190, P.R. China}
\affil{University of Chinese Academy of Sciences, P.R. China}
\author{Changbom Park,}
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
\author{Hyunbae Park, Cristiano G. Sabiu, }
\affil{Korea Astronomy and Space Science Institute, Daejeon 305-348, Korea}
%\author{David H. Weinberg,}
%\affil{Department of Astronomy and CCAPP, The Ohio State University, 140 West 18th Avenue, Columbus, OH 43210, USA}
%\author{Donald P. Schneider,}
%\affil{Department of Astronomy and Astrophysics, The Pennsylvania State University, 
%University Park, PA 16802 }
%\affil{Institute for Gravitation and the Cosmos, The Pennsylvania State University, 
%University Park, PA 16802 }
\author{Juhan Kim\altaffilmark{1},}
\affil{Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 130-722, Korea}
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
\and
\author{Sungwook E. Hong}
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}

@@

\begin{abstract}
We use the redshift dependence of the galaxy angular 2-point correlation function (2pCF) shape 
to constrain cosmological parameters.
A wrongly adopted cosmology introduces redshift-dependent mis-scaling 
of the constructed galaxy distribution,
leading to redshift-dependent rescaling in the measured angular 2pCF.
We test our method on the HR4 mock galaxies having hundreds of millions of galaxies at redshifts 
0, 0.5, 1, 1.5, 2.
We find the redshift evolution of shape of angular 2pCF, as a function of scale,
is sensitive to the adopted cosmological parameters. 
It is relatively insensitive to the gravitational growth of structure,
the galaxy bias, and the redshift space distortion.
Analyzing the 2pCF shape on scales $5  h^{-1} {\rm Mpc} \leq r_\perp \leq 40 h^{-1} {\rm Mpc}$, 
we derive tight constraints on $\Omega_m$ and $w$.
%Our method is complementary to current works using 2pCF to constrain cosmological parameters.
The method could be applicable to future photometric surveys like DES, LSST 
to derive tight cosmological constraints.
The work is a continue of our previous works \citep{Li2014,Li2015,Li2016}
as a strategy to constrain cosmological parameters based on some nearly redshift-invariant physical quantity;
they are all powerful in constrain cosmology and have a lot of merits,
e.g., are less affected by the systematic effects introduced by non-linear clustering or RSD,
does not require accurate modeling of galaxy clustering,
and are applicable on relative small clustering scales.
\end{abstract}

@@

%The  Alcock-Paczynski (AP) effect referes to
%the geometric distortion when incorrect cosmological models are assumed for 
%transforming redshift to comoving distance,
%induced by the fact that measured distances along and perpendicular to the line of sight are fundamentally different.

%The AP effect can be measured through the staistial study of galaxies clustering  \citep{Ballinger1996,Matsubara1996,
%Outram2004,Blake2011,ChuangWang2012,Reid2012,Beutler2013,Linder2013,2014arXiv1407.2257S, Jeong2014,Sutter2014,2014ApJ...781...96L,Alam2016, Beutler2016, Sanchez2016},
%symmetry properties of galaxy pairs \citep{Marinoni2010,Jennings2011,BB2012},
%and cosmic voids \citep{Ryden1995,LavausWandelt1995,Sutter2014,Qingqing2016}.
%The main caveat of these methods is that,
%because the radial distances of galaxies are inferred from redshifts,
%AP tests are inevitably limited by redshift-space distortions (RSD) \citep{Ballinger1996},
%which leads to apparent anisotropy even if the adopted cosmology is correct.

%\cite{Li2014,Li2015,Li2016} proposed a novel strategy to measure the redshift dependence of AP.
%Anisotropies produced by the RSD effect are, although large,
%maintaining a nearly uniform magnitude over a large range of redshift,
%while the degree of anisotropies from the AP effect varies with redshift by much larger magnitude. 
%\citep{Li2016} applies this method to the SDSS-III BOSS DR12 galaxies, and obtained tight cosmological constraints 
%comparable to the mainstream probes of SNIa, BAO or CMB.
%This method could play an important role in deriving cosmological constraints from future LSS surveys.

@@

\begin{figure*}
   \centering{
   \includegraphics[height=8cm]{fig1_a.eps}
   \includegraphics[height=8.5cm]{fig1_b.eps}
   }
   \caption{\label{fig_xyquan}
   A description of how wrongly assumed cosmologies can distort the interpretation of observation,
   assuming $\Omega_m=0.26,w=-1$ is the true cosmology. 
   Left panel shows a series of five regular squares, measured by an observer at the origin.
   Their true positions and shapes are plotted in blue dashed lines.
   When the observer adopts the wrong cosmologies to compute the distance from measured redshifts and infer the positions and shapes of the squares,
   he/she obtains distorted squares shown as the red solid lines.
   Right panel shows the redshift evolution of the wrongly estimated angular diameter distance (divided by the correct value).
   }
   % Need a better plot to show angular size variation!!!
\end{figure*}

@@

In case wrong values of $\Omega_m$ and $w$ are adopted, 
the inferred $\Delta r_{\parallel}$ and $\Delta r_{\perp}$ are wrong,
resulting in wrong estimations of the object's shape (AP effect) and size (volume effect).
These effects and their cosmological consequences have been studied in \cite{Li2014,Li2015,Li2016}.

In this paper we focus on the mis-estimation of the angular size $\Delta r_{\perp}$. %scaling of angular size,
The ratio of mis-estimation is
\begin{equation}\label{eq:DA}
 %{\rm Degree\ of\ volume\ magnification \equiv}
 %{\rm rat}_{\rm volume\ mag}\equiv
 \alpha_{\perp} \equiv \frac{\Delta r_{\perp, \rm wrong}}{\Delta r_{\perp, \rm true}}
 = \frac{D_{A, \rm wrong}}{D_{A, \rm true}},
\end{equation}
where ``true'' and ``wrong'' denote the values in the true cosmology and wrongly assumed cosmologies, respectively.

An illustration is provided in the left panels of Figure \ref{fig_xyquan}.
Suppose that the true cosmology is a flat $\Lambda$CDM with present matter ratio $\Omega_m=0.26$
and standard dark energy EoS $w=-1$.
If we were to distribute a series of perfect squares at distances ranging from 500 Mpc/h to 3\,000 Mpc/h,
and an observer located at the origin were to measure their redshifts and infer the sizes of the squares
using the distance-redshift relations of four incorrect cosmologies
\begin{eqnarray}
 & &{\rm (i)}.\ \Omega_m=0.40,\ w=-1.0, \nonumber \\ 
 & &{\rm (ii)}.\ \Omega_m=0.15,\ w=-1.0, \nonumber\\ \noindent
 & &{\rm (iii)}.\ \Omega_m=0.26,\ w=-0.5,\nonumber\\ \noindent
 & &{\rm (iv)}.\ \Omega_m=0.26,\ w=-1.5,  \nonumber \noindent 
\end{eqnarray}
as a result, 
the shapes of the squares appear distorted (AP effect),
and their sizes are wrongly estimated (volume effect).
Cosmological models (i,iii) yield to compressed size (in both angular and LOS direction),
and the degree of compression increases with increasing distance;
the situation is opposite for the other two cosmologies.

The mis-estimation of angular size, ${\Delta r_{\perp, \rm wrong}}/{\Delta r_{\perp, \rm true}}$, 
is displayed in the right panel of Figure \ref{fig_xyquan}.
In all cosmologies, ${\Delta r_{\perp, \rm wrong}}/{\Delta r_{\perp, \rm true}}$ evolves a lot in the redshift range $0<z<2$.
As an example, when adopting the quintessence cosmology $\Omega_m=0.26,\ w=-0.5$,
the angular size is underestimated by 
%12.5\%, 17.7\%, 20.1\%, 21.3\%
8.9\%, 12.3\%, 13.6\%, 14.1\% 
at $z=0.5,1,1.5,2$.

@@

In sum, as a consequence of incorrect cosmologies, 
the size of objects is mis-estimated, and the magnitude of mis-estimation depends on the redshift.
We use the galaxy angular 2pCF to probe the mis-estimation of angular size, ${\Delta r_{\perp, \rm wrong}}/{\Delta r_{\perp, \rm true}}$.

@@

The resulting mock galaxies was found to reproduce the 2pCF of SDSS DR7 volume-limited galaxy sample \citep{zehavi2011} very well.
The mock galaxies shows a similar finger of god (FOG) feature \citep{FOG} as the observation.
The projected 2pCF of the mock and observational samples agree within 1$\sigma$ CL
on scales greater than 1 ${h^{-1}}$Mpc.

%As will be introduced in the next section, 
%The output of HR4 simulation includes one all-sky light cone mock galaxy catalogue reaching $r=3\,150$ ${h^{-1}}$Mpc 
%and a series ({\bf how many?}) of snapshot mock galaxy catalogues at different redshifts.
We take the snapshot data of the mock galaxies at $z=0,0.5,1,1.5,2$.
%We require subhalos to have at least 30 member particles, 
%so the minimal mass of galaxies is $\simeq m_{p} \simeq 2.7 \times 10^{11} \hMsun$.
Setting a minimal halo mass of $3\times 10^{11} \hMsun$, 
%$4.57\times 10^8$, $4.06\times 10^8$, $3.52\times 10^8$, $3.06\times 10^8$ and $2.28 \times 10^8$ mock galaxies,
we select 457, 406, 352, 206 and 228 million mock galaxies at the five redshifts,
corresponding to a number density of 
%$1.46\times 10^{-2}$, $1.30\times 10^{-2}$, $1.13\times 10^{-2}$, $0.98\times 10^{-2}$ and $0.73\times 10^{-2}\ (h^{-1} \rm Mpc)^{-3}$,
1.46, 1.30, 1.13, 0.98 and 0.73 in unit of $ 10^{-2} h^{3} \rm Mpc^{-3}$,
%$1.46\times 10^{-2}$, $1.30\times 10^{-2}$, $1.13\times 10^{-2}$, $0.98\times 10^{-2}$ and $0.73\times 10^{-2}\ (h^{-1} \rm Mpc)^{-3}$,
respectively.
By applying a uniform mass cut, at higher redshift we have smaller number of galaxies with {\it larger bias}.

As an illustration, Figure \ref{fig_scatter} displays the 2D distribution of a subsample of mock galaxies in five redshifts,
with $x$, $y$ coordinates computed using the ``correct'' cosmological parameters $\Omega_m=0.26,\ w=-1$ (left panels) 
and a set of wrong cosmological parameters $\Omega_m=0.05,\ w=-1.5$ (right panels), respectively.

When the correct cosmology is adopted the cosmic scale is correctly estimated,
the main factor leads to redshift evolution of galaxy distribution is the gravitational growth of structure.
With the decreasing the redshift, we clearly see the clusters and filaments form and grow.
On the other hand, when the wrong cosmology is adopted, there is an artifical scaling of scales in the constructed map.
The separations among galaxies are over-estimated by 
$25.6\%,47.3\%,62.2\%,71.7\%$ at redshifts of $0.5,1.0,1.5,2.5$,
leading to a clear redshift evolution of sizes of structures.

The growth of structure strengths the clustering and make structures more compact,
while the volume effect maintain the clustering pattern and uniformly re-scale the structures on all scales.
Their imprints on the large scale structure is different and should be distinguishable.
In the following, we show that they affect the angular correlation function measurements in different ways, 
and can be easily separated.

@@

\begin{figure*}
   \centering{
   %\includegraphics[height=5.9cm]{fig8_0.eps}
   %\includegraphics[height=5.9cm]{fig8_wrongcos_0.eps}
   %\includegraphics[width=16cm]{fig2.eps}
   %\includegraphics[width=16cm,natwidth=8,natheight=14]{fig2.pdf}
   \includegraphics[width=16cm]{fig2.eps}
   }
   \caption{\label{fig_scatter}
  The 2D distribution of a $260\times130\times105 (h^{-1}{\rm Mpc})^3$ subsample of HR4 mock galaxies, 
  at redshifts 0.5, 1, 1.5 and 2.
  Left and right panels whos the $x$, $y$ coordinates computed using the ``correct'' parameters $\Omega_m=0.26,\ w=-1$ 
  and a set of wrong cosmological parameters $\Omega_m=0.05,\ w=-1.5$, respectively.
  The growth of structure strengths the clustering and make structures more compact at lower redshift.
  When the wrong cosmology is adopted, the covmoving distances is mis-scaled and over-estimated by $25.6\%,47.3\%,62.2\%,71.7\%$ at redshifts of $0.5,1.0,1.5,2.5$,
  leading to a clear redshift evolution of sizes of structures.
   }
   % Need a better plot to show angular size variation!!!
\end{figure*}

@@

We use the angular 2pCF as a statistical tool to probe the volume effect.
The galaxy 2pCF as a function of galaxy separation in the angular direction, $\omega(r_\perp)$, is computed for snapshot data of mock galaxies at redshifts 0.5, 1, 1.5 and 2.
We adopt the Landy-Szalay estimator~\citep{1993ApJ...412...64L},
\begin{equation}
\omega(r_\perp)=\frac{DD-2DR+RR}{RR}\ ,
\end{equation}
where $DD$ is the number of galaxy--galaxy pairs, 
$DR$ the number of galaxy-random pairs, 
and $RR$ is the number of random--random pairs, 
all separated by a distance defined by $r_\perp\pm\Delta_{r_\perp}$ where we choose $\Delta_{r_\perp}=1h^{-1}\rm Mpc$.
The random catalogue consists of unclustered points uniformly distributed in a same size box. 
In an effort to reduce the statistical variance of the estimator, we use 50 times as many random points as we have galaxies.

Considering the large number of galaxies and random points the 2pCF is computed part by part in subsamples with 
size of 1575 $h^{-1}{\rm Mpc}\times 1575\ h^{-1}{\rm Mpc}\times 105\ h^{-1}{\rm Mpc}$.
The sheet shape of the subsample is close to the shape of redshift shells in the real observational case.
The Z direction with thickness $105\ h^{-1}\rm Mpc$ is treated as the radial direction (the $r$ direction) 
and the X-Y directions %with each of width $1575 h^{-1}\ \rm Mpc$ 
are the angular plane.
For our simulation box size we have 120 such subsamples.
The average of the measurements in all subsamples is adopted as the 2pCF of the whole sample,
while the covariances of them are adopted as the covariance matrix (after multiplying a factor of $1/\sqrt{119}$).

\subsection{Galaxy angular 2pCF: at different redshifts}\label{sec_2pCF_diffz}

\begin{figure*}
   \centering{
%   \includegraphics[width=18cm]{fig9_0.eps}
%   \includegraphics[width=18cm]{fig9_1.eps}
%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
%    \includegraphics[height=8cm]{smu.eps}
    \includegraphics[width=18cm]{fig3.eps}
    \includegraphics[width=18cm]{fig3_b.eps}
   }
   \caption{\label{fig_diffz}
  The angular 2pCF ($\omega_{r_\perp}$, left panels), the shape of the angular 2pCF ($\hat{\omega}_{r_\perp}$, middle panels),
  and the evolution with respect to the $z=0$ value ($\hat{\omega}_{r_{\perp}}(z=z_i) - \hat{\omega}_{r_{\perp}}(z=0)$, right panels). 
  Upper panels show that in the correct cosmology the redshift evolution of the shape of 2pCF is rather small, 
  whereas the lower panels show that, in a wrong cosmology $\Omega_m = 0.05,w=-1.5$, the redshift evolution of $\hat{\omega}_{r_\perp}$ is very significant.
   }
\end{figure*}

The upper-left panel of Figure \ref{fig_diffz} displays the angular 2pCF measured from HR4 mock galaxies. % (multiplied by scale $r$) in the five snapshot.
We multiply $\omega$ by the separation $r_\perp$ to have similar size of statistical uncertainty on all scales.

Among different redshifts there is large variation in the amplitude of $\omega(r_\perp)$.
The amplitude is proportional to the clustering strengh which is affected by the gravitational growth of structures and the galaxy bias.
The amplitude is highest at $z=0$ where the structures experienced most growth.
$\omega(r_\perp)$ also increases with redshift at $z>1$ with increasing redshift 
as a reason of increasing galaxy bias.
%leading to stronger clustering strength and higher amplitude of 2pCF.
%On the contrary, at higher redshift we find $\omega(z=2)>\omega(z=1.5)>\omega(z=1)$,
%The trend is different from $z=1,1.5,2$,
%simply because by applying a uniform mass cut we are selecting more biased galaxies at higher redshift.

Different from the large variation of amplitude among different redshifts, 
%The shape of $r_\perp\omega$ also evolves with redshift.
the shape of $r_\perp\omega$ maintains similar at all redshifts;
in general it peaks at $r\sim9 h^{-1}\rm Mpc$ and monotonically drops or increases at larger or smaller scales.
The only exception is the small enhancement at $r\lesssim 2 h^{-1}\rm Mpc$,
which is caused by the non-linear growth of structures 
and is much more significant at lower redshfit.

In order to directly compare the shape of 2pCF at different redshifts,
in the middle panel of Figure \ref{fig_diffz} 
we show the $r_\perp\omega$ normalized by the overall amplitude within 
$5h^{-1}{\rm Mpc} < r < 40h^{-1}{\rm Mpc}$
(here after $\hat \omega_{r_\perp}$):
\begin{equation}
 \hat \omega_{ r_\perp} \equiv  \frac{ {r_\perp\omega}(r_{\perp})}{ \int_{r_{\perp, \rm min}}^{r_{\perp, \rm max}}r_{\perp} \omega(r_{\perp}) d r_{\perp} / (r_{\perp,\rm max}-r_{\perp,\rm min}) },
\end{equation}
where we choose $r_{\perp, \rm min}=5 h^{-1}$ Mpc, $r_{\perp, \rm max}=40 h^{-1}$ Mpc in this analysis.
Below $5 h^{-1}$ Mpc the non-linear growth of structure 
leads to systematic redshift evolution which could be difficult to be reliably accounted;
On scales larger than $40 h^{-1}$ Mpc,
the analytical modelling of the shape of the angular 2pCF is relatively well understood;
one can just fit the 2pCF with the theoretical predictions \citep{Salvador2014,Salvador2016} 
instead of using our method 
(although out method should is also applicable).
